Footpath Planning for Example-driven Procedural Road Networks

### 2020-03-06 paper/paper.tex
Paper: two columns
Add motivation and a few implementation steps to the report

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{float}
\usepackage{hyperref}
\setlength\parindent{0pt}

@@

@@

@@

@@

>>>>

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{float}
\usepackage{hyperref}
\usepackage{multicol}
\setlength\parindent{0pt}

@@

\begin{multicols}{2}

@@

With that said, Nishida et. al. present an excellent solution for generating new road patches that comform to an underlying terrain function.

@@

Motivation

Navigation agents, they might fail navigating when faced with a too narrow path or intersecting obstacles
Using a road network to creates an underlying navmesh

@@

\section(OSM Data)

To separate sidewalks from detached footpaths, I used the fact that OSM generally provides sidewalks with the same name as the adjacent motorway. Thus they can be paired together and measured against each other.

\section{Implementation}

In this implementation, roads of different types were allowed to merge into one another to form common intersections. To facilitate this, it was neccessary to work with a path-by-path representation of the point data. When two path share a node with common coordinates, they form an intersection which can be of multiple different types.

\end{multicols}
